Kernel Smoothing And Heat Equation

### 2021-02-16 latex/draft.tex
update after meeting

@@

\begin{figure}[H]
Plot sample size $N$ versus variance\\
\includegraphics[width=1.55in]{pic/bias1.png}
\includegraphics[width=1.55in]{pic/bias2.png}
\includegraphics[width=1.55in]{pic/bias3.png}
\end{figure}

\begin{figure}[H]
Plot sample size $N$ versus variance\\
\includegraphics[width=2.5in]{pic/bias4.png}
\includegraphics[width=2.5in]{pic/bias5.png}
\end{figure}

>>>>

 % 02/08/2021  
\item 02/08/2021. 
\begin{equation}
         b = \big( \frac{L\sigma^2}{2\sqrt{\pi}(N-1)f''}  \big)^{1/5}
\end{equation}

\begin{figure}[H]
Plot MSE with logbandwidth (left: $y = x^4$; right: $y = \sin(x)$)\\
\includegraphics[width=2.5in]{pic/mse.bw0.png}
\includegraphics[width=2.5in]{pic/mse.bw.png}
\end{figure}

\begin{figure}[H]
Plot MSE with logbandwidth with confidence interval \\($y = \sin(x)$, N = 2001, rep = 200)\\
\includegraphics[width=2.5in]{pic/mse.ci0.png}
\includegraphics[width=2.5in]{pic/mse.ci.png}
\end{figure}

\begin{figure}[H]
Plot sample size $N$ versus bias (using adaptive bandwidth)\\
\includegraphics[width=1.55in]{pic/bias6.png}
\includegraphics[width=1.55in]{pic/bias7.png}
\includegraphics[width=1.55in]{pic/bias8.png}
\end{figure}

\begin{figure}[H]
We notice that when bandwidth is too small or too large, the values fall out of the smooth window (2 left figures: small fixed b; right figure: large fixed b)\\
\includegraphics[width=1.55in]{pic/bias9.1.png}
\includegraphics[width=1.55in]{pic/bias9.2.png}
\includegraphics[width=1.55in]{pic/bias10.png}
\end{figure}

@@

\begin{figure}[H]
Plot sample size $N$ versus bias\\
\includegraphics[width=1.55in]{pic/bias1.png}
\includegraphics[width=1.55in]{pic/bias2.png}
\includegraphics[width=1.55in]{pic/bias3.png}
\end{figure}

\begin{figure}[H]
Plot sample size $N$ versus bias\\
\includegraphics[width=2.5in]{pic/bias4.png}
\includegraphics[width=2.5in]{pic/bias5.png}
\end{figure}

TODOLIST:
\begin{enumerate}
\item find the optimal smoother and redraw the figures. 
\item prove adaptive smoothing is an advantage
\item replace variate kernel smoother to heat equation
\begin{align*}
\frac{\partial u}{\partial t} &= \nabla_x (c(x)\nabla_x u) \\ 
&\approx c(x) \nabla^2 u \\ 
\end{align*}
\item implement finite differential solver (compare diffusion coefficient)
\item long term: finite different method (FDM) and finite element method (FEM) 
\end{enumerate}
